Simulation

### 2022-10-14 Manuscript/manuscript.qmd
Add results of simulation in a table.

@@

*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed.

@@

>>>>

```{r R packages}
#| echo: false
#| message: false

library(dplyr)
library(stringr)
library(here)
library(tibble)
library(ggplot2)
library(gridExtra)
library(patchwork)
library(labelled)
library(gtsummary)
library(flextable)
library(DCVtestkit)
```

@@

*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed. Workflow $1$ uses both the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the dilution curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity). Workflow $2$ goes one step further by using the Mandel’s Fitting Test and the concavity of the fitted quadratic model to check if the non-linear dilution curve plateaus at low concentrations (labelling them as limit of detection) or high concentrations (labelling them as saturation). Non-linear dilution curves that do not follow these trends are then labelled as Poor Linearity.

@@

```{r Load Simulated Data Results}
#| echo: false
saturation_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "saturation_dilution_summary.rds")
)

lod_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "lod_dilution_summary.rds")
)

linear_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "linear_dilution_summary.rds")
)
```

```{r Combine Simulated Data Results}
#| echo: false
saturation_dilution_summary <- saturation_dilution_summary |> 
  dplyr::mutate(curve_group = "Saturated")

lod_dilution_summary <- lod_dilution_summary |> 
  dplyr::mutate(curve_group = "Limit of Detection")

linear_dilution_summary <- linear_dilution_summary |> 
  dplyr::mutate(curve_group = "Linear")

combined_dilution_summary <-
  dplyr::bind_rows(
    saturation_dilution_summary,
    lod_dilution_summary,
    linear_dilution_summary
  ) 
```

```{r Data Wrangling for Simulation Results}
#| echo: false
combined_dilution_summary <- 
  combined_dilution_summary |> 
  dplyr::mutate(
    curve_group = factor(.data$curve_group,
                         levels = c("Linear",
                                    "Saturated",
                                    "Limit of Detection")),
    wf2_group = stringr::str_replace(
      string = .data$wf2_group,
      pattern = "LOD",
      replacement = "Limit of Detection"
    ),
    wf2_group = factor(.data$wf2_group,
                         levels = c("Good Linearity",
                                    "Saturation",
                                    "Limit of Detection",
                                    "Poor Linearity"))
  ) |> 
  labelled::set_variable_labels(
    ID = "Unique Curve Identifier",
    curve_group = "Simulated Curve Group",
    wf1_group = "Workflow 1 Result",
    wf2_group = "Workflow 2 Result",
    r_corr = "Pearson Correlation Coefficient",
    pra_linear = "Percent Residual Accuracy",
    mandel_p_val = "Mandel's Test p Value",
    concavity = "Concavity Of Fitted Quadratic Model",
    r2_linear = "Coefficient Of Determination",
    r2_adj_linear = "Adjusted Coefficient Of Determination",
    mandel_stats = "Test statistics from Mandel's Test"
  )

```

The workflow was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as LOD curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)

```{r}
#| echo: false
#| label: tbl-simulation-result
#| tbl-cap-location: bottom
#| tbl-cap: "Simulation Results"
combined_dilution_summary |> 
  dplyr::select(c("curve_group", "wf2_group", 
                  "r_corr", "pra_linear")) |> 
  gtsummary::tbl_summary(
    by = "curve_group",
    statistic = list(
      wf2_group ~ "{n}/{N} ({p}%)"
    ) 
  ) |> 
  modify_header(all_stat_cols() ~ "**{level}**\nN = {n}") |> 
  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Types**") |>  
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit")

```

### 2022-10-14 Quarto_Simulation/index.qmd
Add results of simulation in a table.

library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(ggplot2)
library(epifitter)
library(deSolve)
library(DCVtestkit)

@@

@@

@@

@@

```{r dilution statistical summary saturated}
saturation_dilution_summary <- DCVtestkit::summarise_dilution_table(
  dilution_table = saturation_simulated_database,
  grouping_variable = c("ID"),
  conc_var = "x",
  signal_var = "y")
```

@@

```{r dilution statistical summary lod}
lod_dilution_summary <- DCVtestkit::summarise_dilution_table(
  dilution_table = lod_simulated_database,
  grouping_variable = c("ID"),
  conc_var = "x",
  signal_var = "y")

@@

@@

```{r dilution statistical summary linear}
linear_dilution_summary <- DCVtestkit::summarise_dilution_table(
  dilution_table = linear_simulated_database,
  grouping_variable = c("ID"),
  conc_var = "x",
  signal_var = "y")

@@

>>>>

library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(ggplot2)
library(epifitter)
library(reactable)
library(deSolve)
library(DCVtestkit)

@@

```{r Save Simulated Data Saturated}
saveRDS(saturation_simulated_database, 
        file = "saturated_simulated_database.rds")
```

@@

```{r Save Simulated Data LOD}
saveRDS(lod_simulated_database, 
        file = "lod_simulated_database.rds")
```

@@

```{r Save Simulated Data Linear}
saveRDS(linear_simulated_database, 
        file = "linear_simulated_database.rds")
```

@@

```{r dilution statistical summary saturated}
#| message: false
saturation_dilution_summary <- 
  DCVtestkit::summarise_dilution_table(
    dilution_table = saturation_simulated_database,
    grouping_variable = c("ID"),
    conc_var = "x",
    signal_var = "y") |> 
  DCVtestkit::evaluate_linearity(
    grouping_variable = c("ID")
  )
```

```{r save dilution statistical summary saturated}
saveRDS(saturation_dilution_summary, 
        file = "saturation_dilution_summary.rds")
```

@@

```{r dilution statistical summary lod}
#| message: false
lod_dilution_summary <- 
  DCVtestkit::summarise_dilution_table(
    dilution_table = lod_simulated_database,
    grouping_variable = c("ID"),
    conc_var = "x",
    signal_var = "y") |> 
  DCVtestkit::evaluate_linearity(
    grouping_variable = c("ID")
  )

@@

```{r save dilution statistical summary lod}
saveRDS(lod_dilution_summary, 
        file = "lod_dilution_summary.rds")
```

@@

```{r dilution statistical summary linear}
#| message: false
linear_dilution_summary <-
  DCVtestkit::summarise_dilution_table(
    dilution_table = linear_simulated_database,
    grouping_variable = c("ID"),
    conc_var = "x",
    signal_var = "y") |> 
  DCVtestkit::evaluate_linearity(
    grouping_variable = c("ID")
  )

@@

```{r save dilution statistical summary linear}
saveRDS(linear_dilution_summary, 
        file = "linear_dilution_summary.rds")
```
